---
title: "Chapter 5 tables and graphs"
output: html_document
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) { 
      out_dir <- "docs";
      if(!file.exists(out_dir)) {dir.create(out_dir)};
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, sprintf("%s.html", basename(tools::file_path_sans_ext(inputFile)))))})
---

```{r setup}
library(data.table)
library(tidyverse)
# library(xtable)
library(countrycode)
# library(magrittr)
# library(jtools)
# library(lmtest)
# library(gridExtra)
# library(pastecs)
# library(plm)
options(scipen = 999)
```


# Prepare the data

Get the data which is created by the `dataprep.R`.


```{r  data preparation}
rm(list = ls())
source("r-codes/dataprep.R")
head(oja_capture)
setkeyv(oja_capture, cols = c("general_id", "idcountry", "grab_date", "expire_date",  
                                  "idesco_level_2", "nace", "source", "source_category", 
                                  "t2018Q3", "t2018Q4", "t2019Q1", "t2019Q2", "t2019Q3", "t2019Q4"))
oja_capture[, occup := substr(idesco_level_2,1,1)]
```


# Figure 17

Distribution of number of advertisements by quarters and days to the end of given quarter based on `grab_date` variable

```{r figure17, fig.height=6,fig.width=8}
# (fig-times-dist.png)
rbind(oja_db[t2018Q3 == TRUE,.N, .(vals=t2018Q3_days)][, quar:="2018Q3"],
      oja_db[t2018Q4 == TRUE,.N, .(vals=t2018Q4_days)][, quar:="2018Q4"],
      oja_db[t2019Q1 == TRUE,.N, .(vals=t2019Q1_days)][, quar:="2019Q1"],
      oja_db[t2019Q2 == TRUE,.N, .(vals=t2019Q2_days)][, quar:="2019Q2"],
      oja_db[t2019Q3 == TRUE,.N, .(vals=t2019Q3_days)][, quar:="2019Q3"],
      oja_db[t2019Q4 == TRUE,.N, .(vals=t2019Q4_days)][, quar:="2019Q4"]) -> times

times %>%
  ggplot(data = ., aes(x = vals, y = N/1000)) +
  geom_col() + 
  facet_wrap(~quar) +
  theme_bw() +
  labs(x = "Days to end of quarte based on grab_date variable", y = "Number of advertisements (in thous.)") -> p
plot(p)
```

# Figure 18

Comparison of estimates based on JVS (solid red line; seasonally unadjusted data), OJA data without trimming (solid black line) and trimmed data (solid gray lines)

```{r figure 18, fig.height=6,fig.width=8}
# (fig-trimed.png)
# Removing number of advertisements based on time -- trimming

stats_quart_2018Q3 <- list()
stats_quart_2018Q4 <- list()
stats_quart_2019Q1 <- list()
stats_quart_2019Q2 <- list()
stats_quart_2019Q3 <- list()
stats_quart_2019Q4 <- list()

days_pass <- c(130,seq(from  = 7, to = 50, by = 1))

for (d in days_pass) {
  stats_quart_2018Q3[[d]] <- oja_capture[ t2018Q3 & t2018Q3_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
  stats_quart_2018Q4[[d]] <- oja_capture[ t2018Q4 & t2018Q4_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
  stats_quart_2019Q1[[d]] <- oja_capture[ t2019Q1 & t2019Q1_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
  stats_quart_2019Q2[[d]] <- oja_capture[ t2019Q2 & t2019Q2_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
  stats_quart_2019Q3[[d]] <- oja_capture[ t2019Q3 & t2019Q3_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
  stats_quart_2019Q4[[d]] <- oja_capture[ t2019Q4 & t2019Q4_days < d, .N, .(general_id, idcountry)][, .N, idcountry]
}

stats_quart_2018Q3_l <- rbindlist(stats_quart_2018Q3, idcol = "remove") %>% mutate(quarter = "2018Q3")
stats_quart_2018Q4_l <- rbindlist(stats_quart_2018Q4, idcol = "remove") %>% mutate(quarter = "2018Q4")
stats_quart_2019Q1_l <- rbindlist(stats_quart_2019Q1, idcol = "remove") %>% mutate(quarter = "2019Q1")
stats_quart_2019Q2_l <- rbindlist(stats_quart_2019Q2, idcol = "remove") %>% mutate(quarter = "2019Q2")
stats_quart_2019Q3_l <- rbindlist(stats_quart_2019Q3, idcol = "remove") %>% mutate(quarter = "2019Q3")
stats_quart_2019Q4_l <- rbindlist(stats_quart_2019Q4, idcol = "remove") %>% mutate(quarter = "2019Q4")

stats_quarts <- bind_rows(stats_quart_2018Q3_l,stats_quart_2018Q4_l,stats_quart_2019Q1_l,stats_quart_2019Q2_l,
                          stats_quart_2019Q3_l,stats_quart_2019Q4_l)

stats_quarts %>%
  left_join(jvs %>% filter(s_adj == "NSA") %>% select(geo, yq, jvs), 
            by = c("quarter" = "yq", "idcountry" = "geo")) %>%
  filter(!is.na(jvs)) %>%
  filter(idcountry != "AT") %>%
  mutate(idcountry = countrycode(idcountry, "eurostat","country.name"))  %>%
  select(idcountry, quarter, oja = N, jvs, remove) %>%
  ggplot(data = .) + 
  geom_line(aes(x = quarter, y = oja/1000, group = remove, alpha = remove)) +
  geom_line(aes(x = quarter, y = jvs/1000, group = 1), color = "red", size = 1.2) + 
  facet_wrap(~idcountry, scales = "free_y") +
  scale_color_brewer(name = "Source", type = "qual", palette = "Set1") +
  theme_bw() +
  labs(x = "Quarter", y = "Job vacancies (in thous.)", alpha = "Days to the \nend of quarter") +
  theme(axis.text.x = element_text(angle = 45, vjust=1,hjust=1)) -> p
plot(p)
```


# Figure 19

Comparison of absolute difference of estimates between OJA trimmed estimates with JVS for each quarter

```{r figure 19, fig.height=6,fig.width=8}
# (fig-trimed-diffs.png)
stats_quarts %>%
  filter(remove != 130) %>%
  left_join(jvs %>% filter(s_adj == "NSA") %>% select(geo, yq, jvs), 
            by = c("quarter" = "yq", "idcountry" = "geo")) %>%
  mutate(bias = abs((N - jvs)/jvs)) %>%
  filter(!idcountry %in% c("AT"))  %>%
  filter(!is.na(jvs)) %>%
  mutate(idcountry = countrycode(idcountry, "eurostat","country.name")) %>%
  ggplot(data = ., aes(x = remove, y = bias, color = quarter, group = quarter)) +
  geom_line()   +
  facet_wrap(~idcountry, scales = "free_y") +
  scale_color_brewer(name  = "Quarter", type = "qual", palette = "Dark2") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) + 
  geom_hline(yintercept = 0, color = "black", type = "dashed") + 
  labs(x = "Days available at the end of quarter", y = "Absolute percentage difference with JVS") -> p

plot(p)
```


