---
title: "Chapter 4 tables and graphs"
output: html_document
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) { 
      out_dir <- "docs";
      if(!file.exists(out_dir)) {dir.create(out_dir)};
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, sprintf("%s.html", basename(tools::file_path_sans_ext(inputFile)))))})
---

```{r setup}
library(xtable)
library(countrycode)
library(magrittr)
library(jtools)
library(lmtest)
library(gridExtra)
library(pastecs)
library(plm)
options(scipen = 999)
```

## Prepare the data

```{r data preparation}
rm(list = ls())
source("r-codes/dataprep.R")
```

## Table 3

Number of observations by quarter in country

```{r table3}
 dcast(oja,countries~time,fun.aggregate=sum,value.var='vals') %>%
  xtable(digits = 0, 
         caption = "Number of advertisements active at the end of each quarter") %>%
  print.xtable(include.colnames = T, include.rownames = F, 
               format.args = list(big.mark = ",", decimal.mark = ""),
               caption.placement = "top")
```

## Table 4

Number of unique data sources overtime

```{r table 4a}
oja_db[idcountry != "UK", lapply(.SD, sum),  keyby = .(idcountry, source), .SDcols = t2018Q3:t2019Q4] %>%
  gather(quarter, vals, t2018Q3:t2019Q4) %>%
  filter(vals >0) %>%
  count(idcountry, quarter) %>%
  spread(quarter, n) %>%
  mutate(idcountry = countrycode(idcountry, "eurostat","country.name")) %>%
  rename(Country="idcountry") %>%
  xtable(digits = 0, 
         caption = "Number of unique sources of advertisements in Cedefop’s OJA dataset, by quarter") %>%
  print.xtable(include.colnames = T, include.rownames = F, 
               format.args = list(big.mark = ",", decimal.mark = ""),
               caption.placement = "top")
```

How stable are data sources?

```{r table 4b}
oja_db[idcountry != "UK", lapply(.SD, sum),  keyby = .(idcountry, source), .SDcols = t2018Q3:t2019Q4] %>%
  gather(quarter, vals, t2018Q3:t2019Q4) %>%
  filter(vals >0) %>%
  add_count(idcountry, source, name  = "vals") %>%
  count(idcountry, source, vals) %>%
  group_by(idcountry) %>%
  summarise(Whole_period = sum(vals == 6), Total = n(), Share = Whole_period/Total*100) %>%
  mutate(idcountry = countrycode(idcountry, "eurostat","country.name")) %>%
  rename(Country="idcountry") %>%
  xtable(digits = 2, 
         caption = "Number of unique sources of advertisements in Cedefop’s OJA dataset, by quarter") %>%
  print.xtable(include.colnames = T, include.rownames = F, 
               caption.placement = "top")
```

# Table 5

For those advertisements observed whole period, how many advertismenets were present on multiple sources?


```{r table5}
rbind(
  oja_db[(t2018Q3), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2018Q3"],
  oja_db[(t2018Q4), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2018Q4"],
  oja_db[(t2019Q1), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2019Q1"],
  oja_db[(t2019Q2), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2019Q2"],
  oja_db[(t2019Q3), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2019Q3"],
  oja_db[(t2019Q4), .N, .(idcountry, general_id, source)][, .N, .(idcountry, general_id)][
  , .N, .(idcountry, times = N)][, quarter := "t2019Q4"]
) -> oja_db_unique_sources


oja_db_unique_sources[order(idcountry,quarter, times)] %>%
  count(idcountry, quarter, times = ifelse(times > 3, 4, times), wt = N)  %>%
  mutate(idcountry = countrycode(idcountry, "eurostat","country.name")) %>%
  group_by(idcountry,  times) %>%
  summarise(n = mean(n)) %>%
  spread(times, n, fill = 0) %>%
  rename(Country="idcountry",'4 and more'="4") %>%
  xtable(digits = 0, 
         caption = "Average number of advertisements occurring on one, two, three and four and more sources advertisements between 2018Q3 and 2019Q4") %>%
  print.xtable(include.colnames = T, include.rownames = F, 
               format.args = list(big.mark = ",", decimal.mark = ""),
               caption.placement = "top")


```


# Figure 2

Number of job ads in the OJA dataset and number of vacancies from JVS at the end of quarter for 16 countries

```{r figure2, fig.height=8,fig.width=12}
# (relations1.jpeg) , out.width="1600px",out.height="829px"

MERGED_a %>%
filter(JVS > 0) %>%
select(-countries) %>%
group_by(time) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) %>%
gather(datasources, value, c(OJA, JVS)) %>%
ggplot() +
geom_line(aes(x = time, y = round(value/1000), colour = datasources, group=datasources)) +
geom_point(aes(x = time, y = round(value/1000), colour = datasources)) +
scale_colour_manual(values = c("#286EB4","#FAA519"), name = "") +
geom_text(aes(label = round(value/1000), x = time, y = round(value/1000)), hjust = 0, vjust = -1 ) +
theme_bw() +
labs(title = "",
     x = "",
     y = "Number of vacancies (in thousands)") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 16),  
      axis.text.y = element_text(colour = "black", size = 16),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black")) 
```



# Figure 3

Mean quarterly number of job ads in OJA data and vacancies in JVS at the end of quarter

```{r figure3, fig.height=8,fig.width=12}
# (relations3.png)

MERGED_a %>%
select(-time) %>%
group_by(countries) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) -> df -> df_plot
  
df <- df %>%
mutate(val = ifelse(JVS != 0, round(((OJA - JVS)/JVS)*100), NA),
       maxval = ifelse(OJA > JVS, OJA, JVS)) %>%
filter(!is.na(val))
  
  
df_plot %>%
gather(datasources, value, 2:3) %>%
mutate(value = ifelse(value == 0, NA, value),
       countries = as.factor(countries)) %>%
ggplot(aes(x = countries, y = value/1000)) +
geom_bar(aes(fill = datasources), stat = "identity", position = "dodge") +
geom_text(data = df, aes(label = paste0(val, "%"), 
                         x = countries, 
                         y = maxval/1000, hjust = 0.5, vjust = -1 ), size = 4) +
theme_bw() +
scale_fill_manual(values = c("#286EB4","#FAA519"), name = "") +
labs(title = "",
     x = "",
     y = "Number of vacancies (in thousands)") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 15, angle = 90),  
      axis.text.y = element_text(colour = "black", size = 16),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black")) 
```

# Figure 4 

Number of job ads from OJA data and vacancies from JVS in countries over time

```{r figure4, fig.height=8,fig.width=12}
# (relations4.jpeg)
MERGED_a %>%
filter(JVS > 0) %>%
gather(datasources, value, c(OJA, JVS)) %>%
ggplot() +
geom_line(aes(x = time, y = round(value/1000), colour = datasources)) +
geom_point(aes(x = time, y = round(value/1000), colour = datasources)) +
scale_colour_manual(values = c("#286EB4","#FAA519"), name = "") +
theme_bw() +
labs(title = "",
     x = "",
     y = "Number of vacancies (in thousands)") +
facet_wrap(~countries, ncol = 4, scales = "free") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 10),  
      axis.text.y = element_text(colour = "black", size = 10),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold", size = 13),
      axis.line = element_line(colour = "black"))
```

# Table 6

Descriptive statistics for OJA data and JVS - countries and time

```{r table6}
MERGED_a %>%
filter(JVS > 0) %>%
select(OJA,JVS) %>%  
stat.desc()
```


# Figure 5

Mean quarterly number of job ads from OJA and vacancies from JVS at the end of quarter across NACE sections

```{r figure5, fig.height=8,fig.width=12}
# (relations9.png)

MERGED_b %>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                        "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                        "Romania", "Slovakia", "Sweden")) %>% 
select(-c(countries, time)) %>%
group_by(nace_r2) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) -> df -> df_plot

df <- df %>%
mutate(val = round(((OJA - JVS)/JVS)*100),
       maxval = ifelse(OJA > JVS, OJA, JVS))


df_plot %>%
gather(datasources, value, c(OJA, JVS)) %>%
ggplot(aes(x = nace_r2, y = value/1000)) +
geom_bar(aes(fill = datasources), stat = "identity", position = "dodge") +
geom_text(data = df, aes(label = paste0(val, "%"), 
                         x = nace_r2, 
                         y = maxval/1000, hjust = 0.5, vjust = -1 ), size = 5) +
theme_bw() +
scale_fill_manual(values = c("#286EB4","#FAA519"), name = "") +
labs(title = "",
     x = "",
     y = "Number of vacancies (in thousands)") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 16),  
      axis.text.y = element_text(colour = "black", size = 16),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"))
```


# Figure 6

Number of job ads from OJA and vacancies from JVS in NACE sections over time

```{r figure6, fig.height=8,fig.width=12}
# (relations10.jpeg)

MERGED_b %>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                        "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                        "Romania", "Slovakia", "Sweden")) %>% 
select(-countries) %>%
group_by(time, nace_r2) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) %>%
gather(datasources, value, c(OJA, JVS)) %>%
ggplot() +
geom_line(aes(x = time, y = round(value/1000), colour = datasources)) +
geom_point(aes(x = time, y = round(value/1000), colour = datasources)) +
scale_colour_manual(values = c("#286EB4","#FAA519"), name = "") +
theme_bw() +
labs(title = "",
     x = "",
     y = "Number of vacancies (in thousands)") +
facet_wrap(~nace_r2, ncol = 4, scales = "free") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 10),  
      axis.text.y = element_text(colour = "black", size = 10),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold", size = 13),
      axis.line = element_line(colour = "black")) 

```

# Table 7

Descriptive statistics for OJA data and JVS - NACE section and time

```{r table7}
MERGED_b %>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                        "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                        "Romania", "Slovakia", "Sweden")) %>% 
select(-countries) %>%
group_by(time, nace_r2)  %>% 
select(OJA,JVS) %>%  
stat.desc()
```


# Figure 7

Mean quarterly number of job ads from OJA and vacancies from JVS for Hungary across ISCO major groups of occupations at the end of quarter

```{r figure7, fig.height=8,fig.width=12}
# (relations14.png)

MERGED_c %>%
filter(countries == "Hungary") %>%
select(-c(countries, time)) %>%
group_by(isco08) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) -> df -> df_plot

df <- df %>%
mutate(val = round(((OJA - JVS)/JVS)*100),
       maxval = ifelse(OJA > JVS, OJA, JVS))

df_plot %>%
gather(datasources, value, 2:3) %>%
mutate(isco08 = factor(isco08),
       datasources = factor(datasources)) %>%
ggplot(aes(x = isco08, y = value)) +
geom_bar(aes(fill = datasources), stat = "identity", position = "dodge") +
geom_text(data = df, aes(label = paste0(val, "%"), 
                         x = isco08, 
                         y = maxval, hjust = 0.5, vjust = -1 ), size = 5) +
theme_bw() +
scale_fill_manual(values = c("#286EB4","#FAA519"), name = "") +
labs(title = "",
     x = "",
     y = "") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 16),  
      axis.text.y = element_text(colour = "black", size = 16),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"))

```


# Figure 8

Number of job ads from Cedefop and vacancies from Eurostat for ISCO major groups of occupations in Hungary over time

```{r figure8, fig.height=8,fig.width=12}
# (relations15.jpeg)

MERGED_c %>%
filter(countries == "Hungary") %>%
select(-countries) %>%
group_by(isco08, time) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) %>%
gather(datasources, value, c(OJA, JVS)) %>%
ggplot() +
geom_line(aes(x = time, y = value, colour = datasources)) +
geom_point(aes(x = time, y = value, colour = datasources)) +
scale_colour_manual(values = c("#286EB4","#FAA519"), name = "") +
theme_bw() +
labs(title = "",
     x = "",
     y = "") +
facet_wrap(~isco08, ncol = 3, scales = "free") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 10),  
      axis.text.y = element_text(colour = "black", size = 10),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold", size = 13),
      axis.line = element_line(colour = "black"))  
```

# Table 8 

Descriptive statistics for OJA and JVS data for Hungary - ISCO major groups of occupation and time
```{r table8}
MERGED_c %>%
filter(countries == "Hungary") %>%
select(-c(countries, time)) %>%
group_by(isco08) %>%
select(OJA,JVS) %>%  
stat.desc()
```  
  
# Figure 9

Regression fit between JVS and OJA

```{r figure9, fig.height=8,fig.width=12}
geos <- MERGED_a

geos  %<>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Estonia", "Germany",
                        "Hungary", "Latvia", "Lithuania", "Luxembourg", "Netherlands",
                        "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Sweden"))

geos_t <- geos %>%
          select(-countries) %>%
          group_by(time) %>%
          summarise_all(funs(mean(., na.rm = T),
                              sum(., na.rm = T)))


cor(geos_t$OJA_sum, geos_t$JVS_sum)

# (relations2.png)

linear <- lm(JVS_sum ~ OJA_sum, data=geos_t)
summary(linear)
effect_plot(linear, pred = OJA_sum, interval = TRUE, plot.points = TRUE)
```


# Figure 10

Regression results between OJA and JVS for individual countries

```{r figure10, fig.height=8,fig.width=12}
# (relations8.jpeg)

df <- MERGED_a  %>%
filter(JVS > 0) %>%
mutate(time = as.character(time))

# custom function

lm_models <- lm_simulator(data = df,
                          dep_var = 4,
                          indep_var = 3,
                          key = 1)

lm_models_models <- lapply(1:16, function(x) lm_models$model_output[[x]]$model)
lm_models_models_plots <- lapply(1:16,  function(x){
  return(
    jtools::effect_plot(lm_models_models[[x]], 
                        pred = OJA , 
                        interval = TRUE, 
                        plot.points = TRUE,
                        main.title = names(lm_models$model_output[x]),
                        colors = "black")
  ) 
})


grid.arrange(lm_models_models_plots[[1]],
             lm_models_models_plots[[2]],
             lm_models_models_plots[[3]],
             lm_models_models_plots[[4]],
             lm_models_models_plots[[5]],
             lm_models_models_plots[[6]],
             lm_models_models_plots[[7]],
             lm_models_models_plots[[8]],
             lm_models_models_plots[[9]],
             lm_models_models_plots[[10]],
             lm_models_models_plots[[11]],
             lm_models_models_plots[[12]],
             lm_models_models_plots[[13]],
             lm_models_models_plots[[14]],
             lm_models_models_plots[[15]],
             lm_models_models_plots[[16]], ncol = 4)
```


# Table 9 

Summary of regression results for individual countries

```{r table9}
lm_models_ols_coefficients <- lapply(1:16, function(x){
return(
cbind(x,
      round(lm_models$model_output[[x]]$intercept),
      format(round(lm_models$model_output[[x]]$beta, digits = 3), nsmall = 3),
      format(round(lm_models$model_output[[x]]$tstat, digits = 2), nsmall = 2),
      "adj.r2" =  format(round(lm_models$model_output[[x]]$adj_r2, digits = 2), nsmall = 2),
      "r2" =  format(round(lm_models$model_output[[x]]$r2, digits = 2), nsmall = 2),
      cbind("stat" = format(round(lm_models$model_output[[x]]$dwtest$statistic, digits = 1), nsmall = 1),
            "val" = lm_models$model_output[[x]]$dwtest$p.value)
      )
)}); 
lm_models_ols_coefficients <- do.call(rbind, lm_models_ols_coefficients)
lm_models_ols_coefficients
```

# Figure 11

Regression results between OJA and JVS for individual economic activities

```{r figure11, fig.height=8,fig.width=12}
# (relations13.jpeg)

df <- MERGED_b %>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                        "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                        "Romania", "Slovakia", "Sweden")) %>% 
select(-countries) %>%
mutate(time = as.character(time)) %>%
group_by(time, nace_r2) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) %>%
ungroup() %>%
select(-time)

# custom function

lm_models <- lm_simulator(data = df,
                          dep_var = 3,
                          indep_var = 2,
                          key = 1)

lm_models_models <- lapply(1:19, function(x) lm_models$model_output[[x]]$model)
lm_models_models_plots <- lapply(1:19,  function(x){
  return(
    jtools::effect_plot(lm_models_models[[x]], 
                        pred = OJA , 
                        interval = TRUE, 
                        plot.points = TRUE,
                        main.title = names(lm_models$model_output[x]),
                        colors = "black")
  ) 
})


grid.arrange(lm_models_models_plots[[1]],
             lm_models_models_plots[[2]],
             lm_models_models_plots[[3]],
             lm_models_models_plots[[4]],
             lm_models_models_plots[[5]],
             lm_models_models_plots[[6]],
             lm_models_models_plots[[7]],
             lm_models_models_plots[[8]],
             lm_models_models_plots[[9]],
             lm_models_models_plots[[10]],
             lm_models_models_plots[[11]],
             lm_models_models_plots[[12]],
             lm_models_models_plots[[13]],
             lm_models_models_plots[[14]],
             lm_models_models_plots[[15]],
             lm_models_models_plots[[16]],
             lm_models_models_plots[[17]],
             lm_models_models_plots[[18]],
             lm_models_models_plots[[19]], ncol = 5) 
```


# Table 10

Summary of regression results for individual economic activities

```{r table10}
lm_models_ols_coefficients <- lapply(1:19, function(x){
return(
cbind(x,
      round(lm_models$model_output[[x]]$intercept),
      format(round(lm_models$model_output[[x]]$beta, digits = 3), nsmall = 3),
      format(round(lm_models$model_output[[x]]$tstat, digits = 2), nsmall = 2),
      "adj.r2" =  format(round(lm_models$model_output[[x]]$adj_r2, digits = 2), nsmall = 2),
      "r2" =  format(round(lm_models$model_output[[x]]$r2, digits = 2), nsmall = 2),
      cbind("stat" = format(round(lm_models$model_output[[x]]$dwtest$statistic, digits = 1), nsmall = 1),
            "val" = lm_models$model_output[[x]]$dwtest$p.value)
    )
)}); 
lm_models_ols_coefficients <- do.call(rbind, lm_models_ols_coefficients)
lm_models_ols_coefficients
```


# Table 11 and Figure 12

Panel data regression between OJA and JVS - countries
--- and ---
Time effects for the fixed effects regression between OJA and JVS
```{r figure12, fig.height=8,fig.width=12}
geos <- MERGED_a
geos[geos == 0] <- NA

geos  %>%
  filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Estonia", "Germany",
                          "Hungary", "Latvia", "Lithuania", "Luxembourg", "Netherlands",
                          "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Sweden")) -> geos 

geos_t <- geos %>%
  select(-countries) %>%
  group_by(time) %>%
  summarise_all(funs(mean(., na.rm = T),
                      sum(., na.rm = T)))

geos_t$rel <- (geos_t$OJA_mean - geos_t$JVS_mean) / geos_t$JVS_mean

geos_s <- geos %>%
  select(-time) %>%
  group_by(countries) %>%
  summarise_all(funs(mean(., na.rm = T),
                      sum(., na.rm = T)))

geos_s$rel <- (geos_s$OJA_mean - geos_s$JVS_mean) / geos_s$JVS_mean

geos <- pdata.frame(geos, index=c("countries","time"), stringsAsFactors = TRUE)

panel1 <- plm(JVS ~ OJA, data=geos, model="within", effect = "twoways")
summary(panel1)
pdwtest(panel1)
fixed <- fixef(panel1, effect = "time")                                                
fixef(panel1, effect = "individual")
plot(fixed)

panel2 <- plm(JVS ~ OJA, data=geos, model="random", effect = "twoways")
summary(panel2)
pdwtest(panel2)
phtest(panel1,panel2)
ranef(panel2)

panel3 <- plm(JVS ~ OJA, data=geos, model="fd", effect = "individual")
summary(panel3)
pdwtest(panel3)

```

# Figure 13

Fixed effects regression between OJA and JVS with increasing time span

```{r figure13, fig.height=8,fig.width=12}

# countries over the time 
df_countries <- MERGED_a %>%
                filter(JVS > 0)

unique_time <- unique(df_countries$time)
models_countries <- lapply(2:length(unique(df_countries$time)) , function(x){
sample <- df_countries[df_countries$time %in% unique_time[1:x],]  
m <- plm("JVS ~ OJA", data = sample, index = c("countries", "time"), effect = "twoways", model = "within")  
fixef <- fixef(m)
beta <- m$coefficients
return(list("model" = m, "beta" = beta, "fixedeffect" = fixef))
}); names(models_countries) <- paste0(2:length(unique(df_countries$time)), " years", sep = "")
# objects in list: 1 - model, 2 - only beta's, 3 - vector of fixed effect for the entire list of countries

# NACE over the time 
df_nace <- MERGED_b %>%
filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                        "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                        "Romania", "Slovakia", "Sweden")) %>% 
select(-countries) %>%
group_by(nace_r2, time) %>%
summarise(across(.cols = everything(),~ sum(., na.rm = T))) %>%
ungroup()

unique_time <- unique(df_nace$time)
models_nace <- lapply(2:length(unique(df_nace$time)) , function(x){
sample <- df_nace[df_nace$time %in% unique_time[1:x],]  
m <- plm("JVS ~ OJA", data = sample, index = c("nace_r2", "time"), effect = "twoways", model = "within")  
fixef <- fixef(m)
beta <- m$coefficients
return(list("model" = m, "beta" = beta, "fixedeffect" = fixef))
}); names(models_nace) <- paste0(2:length(unique(df_nace$time)), " years", sep = "")
# objects in list: 1 - model, 2 - only beta's, 3 - vector of fixed effect for the entire list of countries


# merge models
df_countries <- lapply(1:length(models_countries), 
                       function(x) models_countries[[x]]$beta); df_countries <- do.call(rbind, df_countries)
df_countries  <- cbind(seq(2,6,1), df_countries)
df_nace <- lapply(1:length(models_nace), 
                  function(x) models_nace[[x]]$beta); df_nace <- do.call(rbind, df_nace)
df_nace  <- cbind(seq(2,6,1), df_nace)

df <- cbind(df_countries,df_nace[,2]) %>% data.frame()
colnames(df) <- c("index", "Countries", "NACE")

# Fixed effects regression between OJA and JVS with increasing time span
df %>%
gather(org, value, 2:3) %>% 
ggplot() +
geom_line(aes(x = index, y = value, colour = org)) +
geom_point(aes(x = index, y = value, colour = org)) +
geom_text(aes(label = format(round(value, 3), nsmall = 3) , x = index, y = value), hjust = 0, vjust = -1 ) +
scale_colour_manual(values = c("#286EB4","#FAA519"), name = "") +
theme_bw() +
labs(title = "",
       x = "",
       y = "") +
theme(title = element_text(face = "bold", size = 15),
        axis.text.x = element_text(colour = "black", size = 16),  
        axis.text.y = element_text(colour = "black", size = 16),
        axis.title.y = element_text(vjust = 2),
        legend.text=element_text(size = 16),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black")) 




# plot with error bars in file "plm models.R"
# (relations6.jpeg)

df_countries <- MERGED_a %>%
                filter(JVS > 0)

unique_time <- unique(df_countries$time)
models_countries <- lapply(2:length(unique(df_countries$time)) , function(x){
 sample <- df_countries[df_countries$time %in% unique_time[1:x],]  
 m <- plm("JVS ~ OJA", data = sample, index = c("countries", "time"), effect = "twoways", model = "within")  
 fixef <- fixef(m)
 beta <- m$coefficients
 se <- summary(m)$coefficients[2]
 return(list("model" = m, "beta" = beta, "se" = se, "fixedeffect" = fixef))
}); names(models_countries) <- paste0(2:length(unique(df_countries$time)), " years", sep = "")
# objects in list: 1 - model, 2 - only beta's, 3 - vector of fixed effect for the entire list of countries

# NACE over the time 
df_nace <- MERGED_b %>%
 filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany", "Hungary", 
                         "Latvia", "Lithuania", "Luxembourg", "Netherlands", "Poland", 
                         "Romania", "Slovakia", "Sweden")) %>% 
 select(-countries) %>%
 group_by(nace_r2, time) %>%
 summarise_each(funs(sum(., na.rm = T))) %>%
 ungroup()

unique_time <- unique(df_nace$time)
models_nace <- lapply(2:length(unique(df_nace$time)) , function(x){
 sample <- df_nace[df_nace$time %in% unique_time[1:x],]  
 m <- plm("JVS ~ OJA", data = sample, index = c("nace_r2", "time"), effect = "twoways", model = "within")  
 fixef <- fixef(m)
 beta <- m$coefficients
 se <- summary(m)$coefficients[2]
 return(list("model" = m, "beta" = beta, "se" = se, "fixedeffect" = fixef))
}); names(models_nace) <- paste0(2:length(unique(df_nace$time)), " years", sep = "")
# objects in list: 1 - model, 2 - only beta's, 3 - vector of fixed effect for the entire list of countries



# merge models
df_countries <- lapply(1:length(models_countries), function(x){
 data.frame("beta" = models_countries[[x]]$beta,  "se" = models_countries[[x]]$se)
 }); df_countries <- do.call(rbind, df_countries)
df_countries  <- cbind("lp" = seq(2,6,1), df_countries, "Group" = "Countries")


df_nace <- lapply(1:length(models_nace), function(x) {
 data.frame("beta" = models_nace[[x]]$beta,  "se" = models_nace[[x]]$se)
  }); df_nace <- do.call(rbind, df_nace)
df_nace  <- cbind("lp" = seq(2,6,1), df_nace, "Group" = "NACE")

df <- rbind(df_countries, df_nace)
df <- df %>%
      select(1,4,2,3)

ggplot(df, aes(x = lp, y = beta)) + 
 geom_line() +
 geom_point() +
 geom_errorbar(aes(ymin = beta - se, ymax = beta + se), width=.2,
               position = position_dodge()) + 
 geom_text(aes(label = format(round(beta, 3), nsmall = 3) , x = lp, y = beta), hjust = -0.1, vjust = -0.7, size = 4) +
 facet_wrap(~Group, ncol = 2) +
 theme_bw() +
 labs(title = "",
       x = "",
       y = "") +
 theme(title = element_text(face = "bold", size = 15),
        axis.text.x = element_text(colour = "black", size = 16),  
        axis.text.y = element_text(colour = "black", size = 16),
        axis.title.y = element_text(vjust = 2),
        legend.text=element_text(size = 16),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(colour = "black", size = 16, face = "bold"),
        axis.line = element_line(colour = "black"))
```



# Figure 14

Individual country effects in fixed effects regression between OJA and JVS with increasing time span

```{r figure14, fig.height=8,fig.width=12}
# (relations7.jpeg)

df_countries_beta <- lapply(1:length(models_countries), 
                     function(x) models_countries[[x]]$fixedeffect); df_countries_beta <- do.call(cbind, df_countries_beta)
df_countries_beta <- cbind(rownames(df_countries_beta), df_countries_beta) %>% data.frame()
colnames(df_countries_beta) <- c("countries", "2", "3", "4", "5", "6")

df_countries_beta %>%
gather(index, value, 2:6) %>%
mutate(countries = as.character(countries),
       index = as.numeric(index),
       value = as.numeric(value),
       value = round(value)) %>%
ggplot() +
geom_line(aes(x = index, y = value)) +
geom_point(aes(x = index, y = value)) +
theme_bw() +
labs(title = "",
       x = "",
       y = "") +
facet_wrap(~countries, ncol = 4, scales = "free") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 10),  
      axis.text.y = element_text(colour = "black", size = 10),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold", size = 13),
      axis.line = element_line(colour = "black"))
```



# Table 12 and Figure 15

Panel data regression between OJA and JVS - NACE sections  
---- and  ----
Time effects for the fixed effects regression between OJA and JVS
```{r figure15, fig.height=8,fig.width=12}
nace <- MERGED_b

nace  %>%
  filter(countries %in% c("Bulgaria", "Croatia", "Czechia", "Germany",
                          "Hungary", "Latvia", "Lithuania", "Luxembourg", "Netherlands",
                          "Poland", "Romania", "Slovakia", "Sweden")) -> nace 

nace2 <- nace %>%
  select(-countries) %>%
  group_by(nace_r2, time) %>%
  summarise_all(funs(sum(., na.rm = T))) %>%
  ungroup()

nace_s <- nace %>%
  select(-c(time, countries)) %>%
  group_by(nace_r2) %>%
  summarise_all(funs(mean(., na.rm = T),
                      sum(., na.rm = T)))


nace_s$rel <- (nace_s$OJA_mean - nace_s$JVS_mean) / nace_s$JVS_mean


nace <- pdata.frame(nace2, index=c("nace_r2","time"), stringsAsFactors = TRUE)

panel1 <- plm(JVS ~ OJA, data=nace, model="within", effect = "twoways")
summary(panel1)
pdwtest(panel1)
fixed <- fixef(panel1, effect = "time")                                                
fixef(panel1, effect = "individual")
plot(fixed)

panel2 <- plm(JVS ~ OJA, data=nace, model="random", effect = "twoways")
summary(panel2)
pdwtest(panel2)
phtest(panel1,panel2)
ranef(panel2)

panel3 <- plm(JVS ~ OJA, data=nace, model="fd", effect = "individual")
summary(panel3)
pdwtest(panel3)

```

# Figure 16

Individual industry effects in fixed effects regression between OJA and JVS with increasing time span

```{r figure16, fig.height=8,fig.width=12}
# (relations12.jpeg)

df_nace_beta <- lapply(1:length(models_nace), 
                function(x) models_nace[[x]]$fixedeffect); df_nace_beta <- do.call(cbind, df_nace_beta)
df_nace_beta <- cbind(rownames(df_nace_beta), df_nace_beta) %>% data.frame()
colnames(df_nace_beta) <- c("NACE", "2", "3", "4", "5", "6")

df_nace_beta %>%
gather(index, value, 2:6) %>%
mutate(NACE = as.character(NACE),
         index = as.numeric(index),
         value = as.numeric(value),
         value = round(value)) %>%
ggplot() +
geom_line(aes(x = index, y = value)) +
geom_point(aes(x = index, y = value)) +
theme_bw() +
labs(title = "",
     x = "",
     y = "") +
facet_wrap(~NACE, ncol = 4, scales = "free") +
theme(title = element_text(face = "bold", size = 15),
      axis.text.x = element_text(colour = "black", size = 10),  
      axis.text.y = element_text(colour = "black", size = 10),
      axis.title.y = element_text(vjust = 2),
      legend.text=element_text(size = 16),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold", size = 13),
      axis.line = element_line(colour = "black"))
```


# Table 13

Panel data regression between OJA and JVS - ISCO major groups in Hungary

```{r table13}
isco <- MERGED_c

isco  %>%
  filter(countries %in% c("Hungary")) -> isco 

isco2 <- isco %>%
  select(-countries) %>%
  group_by(isco08, time) %>%
  summarise_all(funs(sum(., na.rm = T))) %>%
  ungroup()

isco_s <- isco %>%
  select(-c(time, countries)) %>%
  group_by(isco08) %>%
  summarise_all(funs(mean(., na.rm = T),
                      sum(., na.rm = T)))


isco_s$rel <- (isco_s$OJA_mean - isco_s$JVS_mean) / isco_s$JVS_mean


isco <- pdata.frame(isco2, index=c("isco08","time"), stringsAsFactors = TRUE)

panel1 <- plm(JVS ~ OJA, data=isco, model="within", effect = "twoways")
summary(panel1)
pdwtest(panel1)
fixed <- fixef(panel1, effect = "time")                                                
fixef(panel1, effect = "individual")
plot(fixed)

panel2 <- plm(JVS ~ OJA, data=isco, model="random", effect = "twoways")
summary(panel2)
pdwtest(panel2)
phtest(panel1,panel2)
ranef(panel2)

panel3 <- plm(JVS ~ OJA, data=isco, model="fd", effect = "individual")
summary(panel3)
pdwtest(panel3)

```

